Model checking for simplified Naomi

### 2023-05-18 src/naomi-simple_model-checks/model-checks.Rmd
Add placeholder histograms and ECDF difference plots (still need to compute "realised" data) #43

```{r}
#' Yes!
```

>>>>

```{r}
tmb <- readRDS("depends/tmb.rds")

indicators <- naomi::add_output_labels(tmb$outputs) %>%
  left_join(tmb$outputs$meta_area %>% select(area_level, area_id, center_x, center_y)) %>%
  sf::st_as_sf()

indicators %>%
  filter(
    sex %in% c("male", "female"),
    age_group == "Y015_049",
    indicator == "prevalence",
    area_level == 4
  ) %>%
  ggplot(aes(fill = mode)) +
  geom_sf() +
  viridis::scale_fill_viridis(labels = scales::percent_format()) +
  naomi::th_map() +
  facet_wrap(~sex)

indicators_fine <- indicators %>%
  filter(
    indicator %in% c("incidence", "prevalence", "art_coverage"),
    area_id %in% paste0("MWI_4_", 1:32, "_demo"),
    sex %in% c("male", "female"),
    age_group %in%
      c(
        "Y000_004", "Y005_009", "Y010_014", "Y015_019", "Y020_024", "Y025_029",
        "Y025_034", "Y030_034", "Y035_039", "Y040_044", "Y045_049", "Y050_054",
        "Y055_059", "Y060_064", "Y065_069", "Y070_074", "Y075_079", "Y080_999"
      )
  )
```

```{r}
mf_out <- tmb$naomi_data$mf_out

mf_out_fine <- mf_out %>%
  tibble::rownames_to_column("id") %>%
  mutate(id = as.numeric(id)) %>%
  filter(
    area_id %in% paste0("MWI_4_", 1:32, "_demo"),
    sex %in% c("male", "female"),
    age_group %in%
      c(
        "Y000_004", "Y005_009", "Y010_014", "Y015_019", "Y020_024", "Y025_029",
        "Y025_034", "Y030_034", "Y035_039", "Y040_044", "Y045_049", "Y050_054",
        "Y055_059", "Y060_064", "Y065_069", "Y070_074", "Y075_079", "Y080_999"
      )
  )

nrow(indicators_fine) / nrow(mf_out_fine)
```

```{r}
get_prob_quantile <- function(indicator) {
  samples <- tmb$fit$sample[[indicator]][mf_out_fine$id, ]
  S <- ncol(samples)
  prob_quantile <- apply(samples, MARGIN = 1, function(x) {
    estimate <- x[1] # This is wrong! I am just using the first sample as a placeholder
    sample_row <- x[1:S]
    if(all(is.na(sample_row))) return(NA)
    else ecdf(sample_row)(estimate)
  })
  data.frame(indicator = indicator, prob_quantile = prob_quantile)
}

df <- lapply(list("rho_t1_out", "lambda_t1_out", "alpha_t1_out"), get_prob_quantile) %>%
  bind_rows()

bins <- 20
alpha <- 0.05

ci <- qbinom(
  p = c(alpha / 2, 0.5, (1 - alpha / 2)),
  size = S,
  prob = 1 / bins
)

polygon_data <- data.frame(
  x = c(-0.05, 0, 1, 0, -0.05, 1.05, 1, 1.05, -0.05),
  y = c(ci[1], ci[2], ci[2], ci[2], ci[3], ci[3], ci[2], ci[1], ci[1]) / S
)

fct_reorg <- function(fac, ...) {
  fct_recode(fct_relevel(fac, ...), ...)
}

histograms <- df %>%
  mutate(indicator = fct_reorg(indicator, "HIV Prevalence" = "rho_t1_out", "HIV Incidence" = "lambda_t1_out", "ART Coverage" = "alpha_t1_out")) %>%
  ggplot(aes(x = prob_quantile)) +
  facet_grid(~indicator, drop = TRUE, scales = "free", labeller = labeller(indicator = label_wrap_gen(20))) +
  geom_histogram(aes(y = (..count..) / tapply(..count..,..PANEL..,sum)[..PANEL..]),
                 breaks = seq(0, 1, length.out = bins + 1), fill = "#009E73", col = "black", alpha = 0.9) +
  geom_polygon(data = polygon_data, aes(x = x, y = y), fill = "grey75", color = "grey50", alpha = 0.6) +
  labs(x = "", y = "") +
  scale_x_continuous(breaks = c(0, 0.25, 0.5, 0.75, 1), labels = c(0, 0.25, 0.5, 0.75, 1)) +
  theme_minimal()

lims <- multi.utils::get_lims(n = S, alpha, K = 100)

ecdf_diff <- df %>%
  split(.$indicator) %>%
  lapply(function(y) {
    empirical_coverage <- purrr::map_dbl(seq(0, 1, by = 0.01), ~ empirical_coverage(y$prob_quantile, .x))
    data.frame(nominal_coverage = seq(0, 1, by = 0.01), empirical_coverage = empirical_coverage) %>%
      mutate(
        ecdf_diff = empirical_coverage - nominal_coverage,
        ecdf_diff_lower = lims$lower / S - nominal_coverage,
        ecdf_diff_upper = lims$upper / S - nominal_coverage,
      )
  }) %>%
  purrr::map_df(~as.data.frame(.x), .id = "indicator") %>%
  mutate(indicator = fct_reorg(indicator, "HIV Prevalence" = "rho_t1_out", "HIV Incidence" = "lambda_t1_out", "ART Coverage" = "alpha_t1_out")) %>%
  ggplot(aes(x = nominal_coverage, y = ecdf_diff)) +
  facet_grid(~indicator, drop = TRUE, scales = "free", labeller = labeller(indicator = label_wrap_gen(20))) +
  geom_line(col = "#009E73") +
  geom_step(aes(x = nominal_coverage, y = ecdf_diff_upper), alpha = 0.7, col = "grey50") +
  geom_step(aes(x = nominal_coverage, y = ecdf_diff_lower), alpha = 0.7, col = "grey50") +
  geom_abline(intercept = 0, slope = 0, linetype = "dashed", col = "grey75") +
  labs(x = "", y = "ECDF difference") +
  scale_x_continuous(breaks = c(0, 0.25, 0.5, 0.75, 1), labels = c(0, 0.25, 0.5, 0.75, 1)) +
  theme_minimal()

pdf("coverage.pdf", h = 4, w = 6.25)

histograms / ecdf_diff

dev.off()

histograms / ecdf_diff
```

Next steps here are:

* Add column to `indicators` with the "raw" value of the indicator and replace the placeholder `estimate <- sample[1]`
* Should probably put the value of `prob_quantile` into the `indicators` dataframe as well
